### 2024-03-22 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

@@

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>79</td><td>12193</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>11476</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>32</td><td>11174</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>10835</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>13</td><td>10360</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>

>>>>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

@@

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>15</td><td>13103</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>11728</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>11427</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>56</td><td>11393</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>36</td><td>11366</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
